---
title: "Debs"
author: "mbh038"
date: "Wednesday, June 24, 2015"
output: html_document
---

```{r load packages}
setwd("C:/Users/Mike/Rspace/Debs")
library(ggplot2)
library(tidyr)
library(dplyr)
```
##Training Budget
```{r training budget}
tb<-data.frame("Category"=c("Pay costs","Devolved to depts. for CPD","Central Funding"),"Allocation"=c(27,33,39))
```
Plot the data
```{r plot the data}
png("budgetallocation.png",width = 680, height = 480)
d<-ggplot(data=tb,
        aes(x=Category, y=Allocation,fill=Allocation, order=-Allocation))+
        geom_bar(stat="identity")+
        #facet_wrap(~variable)+
        coord_flip()+
        scale_y_continuous(breaks = seq(0, 50, 10))+
        theme(axis.text.x = element_text(size=16),
        axis.text.y=element_text(size=14))+
        labs(y = "% Allocation of total training budget")+
        theme(axis.title.x = element_text(size=16,vjust=-.5),
        axis.title.y=element_blank())+
       # theme(legend.text=element_text(size=12),
               # legend.title = element_blank())+
        theme(legend.position="none")
d
dev.off() 
```


##LEARNING AND TEACHING 

KPI        Current Position  %	Headcount 
Post grad qualification	57	85
Teaching qualification or equiv ( HEA Fellow) 	27	40
HEA membership	18	27
Falmouth University May 2015 % of academic staff. 

```{r kpi table}
kpi<-data.frame("Qualification"=c("Post grad qual.","Teaching qual.or equiv (HEA Fellow)","HEA membership"),
                "CurrentPosition"=c(57,27,18),
                "Headcount"=c(85,40,27))
kpitidy<-gather(kpi,CurrentPosition,Headcount,-Qualification)
```
Plot the data
```{r plot kpi data}

count_names <- list(
  'count#1'="Current Position %",
  'count#2'="Head Count"
  )

count_labeller <- function(variable,value){
  return(count_names[value])
}

png("headcount.png",width = 680, height = 480)
d<-ggplot(data=kpitidy,
        aes(x=Qualification, y=Headcount,fill=CurrentPosition))+
        geom_bar(stat="identity")+
        facet_grid(CurrentPosition~.,labeller=count_labeller)+
        #coord_flip()+
        scale_y_continuous(breaks = seq(0, 100, 10))+
        theme(axis.text.x = element_text(size=16),
        axis.text.y=element_text(size=14))+
        labs(title = "Falmouth University May 2015 % of academic staff")+
        theme(title=element_text(size=16,vjust=1.5))+
        theme(axis.title.x = element_text(size=16,vjust=-.5),
        axis.title.y=element_blank())+
       # theme(legend.text=element_text(size=12),
               # legend.title = element_blank())+
        theme(legend.position="none")+
         theme(strip.text.y = element_text(size=12, face="bold"))
d
dev.off() 
```
##WORKFORCE PROFILE

Falmouth University has a headcount of  647  academic 279 and professional services 222 . AL headcount is 124 representing a 19% of the total workforce

```{r workforce profile}
workforce<-data.frame("Category"=c("Academic","Prof. Services","AL"),"Number"=c(279,222,124))
g<-ggplot(data=workforce,aes(x=,y=Number))+geom_bar()
g
```

